### 2025-11-12 mixed-models.qmd
20251112 - fix plot

```{r}
#| label: fig-bayesianRegressionCoefficientsDistributions
#| fig-cap: "Distributions of Regression Coefficients with 66% (Thin Line) and 95% (Thin Line) Credible Intervals from Bayesian Mixed Model."
#| fig-alt: "Distributions of Regression Coefficients with 66% (Thin Line) and 95% (Thin Line) Credible Intervals from Bayesian Mixed Model."

bayesianMixedModelFit %>%
  tidybayes::tidy_draws() %>%
  select(starts_with("b_")) %>%
  pivot_longer(
    everything(),
    names_to = "term",
    values_to = "estimate") %>%
  mutate(term = sub("^b_", "", term)) %>%
  ggplot(
    aes(
      x = estimate,
      y = term)) +
  stat_halfeye() + # by default, .width shows the 66% (thick line) and 95% (thin line) credible intervals
  labs(
    title = "Posterior Distributions of Regression Coefficients with 66% and 95% Credible Intervals",
    x = "Predictor",
    y = "Posterior Estimate") +
  theme_minimal()
```

>>>>

```{r}
#| label: fig-bayesianRegressionCoefficientsDistributions
#| fig-cap: "Distributions of Regression Coefficients with 66% (Thick Line) and 95% (Thin Line) Credible Intervals from Bayesian Mixed Model."
#| fig-alt: "Distributions of Regression Coefficients with 66% (Thick Line) and 95% (Thin Line) Credible Intervals from Bayesian Mixed Model."

bayesianMixedModelFit %>%
  tidybayes::tidy_draws() %>%
  select(starts_with("b_")) %>%
  pivot_longer(
    everything(),
    names_to = "term",
    values_to = "estimate") %>%
  mutate(term = sub("^b_", "", term)) %>%
  ggplot(
    aes(
      x = estimate,
      y = term)) +
  stat_halfeye() + # by default, .width shows the 66% (thick line) and 95% (thin line) credible intervals
  labs(
    title = "Posterior Distributions of Regression Coefficients\nwith 66% and 95% Credible Intervals",
    x = "Predictor",
    y = "Posterior Estimate") +
  theme_minimal()
```
